\plaintitle

### 2016-09-09 Paper/proceedings.tex
Paper Outline

>>>>

One of the motivating examples for the power of information visualization is Anscombe's quartet\cite{anscombe1973graphs}, a set of four bivariate sets with nearly identical summary statistics, but with drastically different patterns when drawn as a scatterplot. Implicit in this example is that people have a robust ability to recognize visual patterns in information visualizations and, moreover, to employ this pattern recognition ability towards statistical ends. That is, an underlying assumption in information visualization is that people have the ability to \emph{visually} estimate \emph{statistical} quantities of interest, and can perform at least rough analogs of statistical tasks including model selection, identification of outliers, and estimation of summary statistics, entirely through visual inspection. Knowing the limits of this ``estimation by eye,'' is important for designers of information visualizations seeking to communicate statistical quantities, especially to the general audience.

In this work, we examine
